\begin{thebibliography}{1}
\bibitem {ODoH-RFC-1}
https://datatracker.ietf.org/doc/rfc9230/

\bibitem {cantrell1}
W. H. Cantrell, ``Tuning analysis for the high-Q class-E power
amplifier,'' \emph{IEEE Trans. Microwave Theory \& Tech.}, vol. 48,
no. 12, pp. 2397-2402, December 2000.

\bibitem {pervasive-monitoring}
S. Farrel and H. Tschofenig. 2014. Pervasive Monitoring Is an Attack. RFC 7258.
RFC Editor. 1–6 pages. https://tools.ietf.org/pdf/rfc7258.pdf

\bibitem {dns-consideration}
S Bortzmeyer. 2015. DNS Privacy Considerations. RFC 7626. RFC Editor. 1–17 pages. https://tools.ietf.org/html/rfc7626

\bibitem {dns-sec}
Arends, R., Austein, R., Larson, M., Massey, D., and S. Rose, "DNS Security Introduction and Requirements", RFC 4033, DOI 10.17487/RFC4033, March 2005, <https://www.rfc-editor.org/info/rfc4033>.

\bibitem {dnscrypt}
F. Denis, “DNSCrypt Specification,” June 2020, https://github.com/DNSCrypt/dnscrypt-protocol/blob/ master/DNSCRYPT-V2-PROTOCOL.txt

\bibitem {dnscrypt-dnssec-def}
Nowaczewski, Slawomir, and Wojciech Mazurczyk. 2021. "Improving Security of Future Networks Using Enhanced Customer Edge Switching and Risk-Based Analysis" Electronics 10, no. 9: 1107. https://doi.org/10.3390/electronics10091107

\bibitem {dot-rfc}
Hu, Z., Zhu, L., Heidemann, J., Mankin, A., Wessels, D., and P. Hoffman, "Specification for DNS over Transport Layer Security (TLS)", RFC 7858, DOI 10.17487/RFC7858, May 2016, <https://www.rfc-editor.org/info/rfc7858>.

\bibitem {doh-rfc}
Hoffman, P. and P. McManus, "DNS Queries over HTTPS (DoH)", RFC 8484, DOI 10.17487/RFC8484, October 2018, <https://www.rfc-editor.org/info/rfc8484>.

\bibitem {analyze-doh-dot}
Timm Böttger, Felix Cuadrado, Gianni Antichi, Eder Leão Fernandes, Gareth Tyson, Ignacio Castro, and Steve Uhlig. 2019. An Empirical Study of the Cost of DNS-over-HTTPS. In Proceedings of the Internet Measurement Conference (IMC '19). Association for Computing Machinery, New York, NY, USA, 15–21. https://doi.org/10.1145/3355369.3355575

\bibitem {http-usage}
2019. A Nonprofit Certificate Authority Providing TLS Certificates to 225 Million Websites.: 2019 Annual Report.
Retrieved October 29, 2020 from https://abetterinternet.org/documents/2019-ISRG-Annual-Report-Desktop.pdf.

\bibitem {tls-usage}
2019. TLS 1.3: One Year Later. Retrieved October 29, 2020 from https://www.ietf.org/blog/tls13-adoption/

\bibitem {website-fingerprint1}
Kevin P. Dyer, Scott E. Coull, Thomas Ristenpart, and Thomas Shrimpton. 2012.
Peek-a-Boo, I Still See You: Why Efficient Traffic Analysis Countermeasures Fail.
In 2012 IEEE Symposium on Security and Privacy. IEEE, San Francisco, CA, USA,
332–346.

\bibitem {website-fingerprint2}
Xiang Cai, Xin Cheng Zhang, Brijesh Joshi, and Rob Johnson. 2012. Touching
from a distance: website fingerprinting attacks and defenses. In Proceedings of
the 2012 ACM Conference on Computer and Communications Security (CCS ’12).
Raleigh, North Carolina, USA.

\bibitem {website-fingerprint3}
Andriy Panchenko, Fabian Lanze, Andreas Zinnen, Martin Henze, Jan Pennekamp,
Klaus Wehrle, and Thomas Engel. 2016. Website Fingerprinting at Internet Scale.
In Proceedings 2016 Network and Distributed System Security Symposium. Internet
Society, San Diego, CA.

\bibitem {website-fingerpring-4}
Rimmer, V., Preuveneers, D., Juarez, M., Van Goethem, T., \& Joosen, W. (2017). Automated Website Fingerprinting through Deep Learning. arXiv. https://doi.org/10.14722/ndss.2018.23105

\bibitem {website-fingerpring-5}
Payap Sirinam, Mohsen Imani, Marc Juarez, and Matthew Wright. 2018. Deep Fingerprinting: Undermining Website Fingerprinting Defenses with Deep Learning. In Proceedings of the 2018 ACM SIGSAC Conference on Computer and Communications Security (CCS '18). Association for Computing Machinery, New York, NY, USA, 1928–1943. https://doi.org/10.1145/3243734.3243768

\bibitem {odoh-paper}
{Singanamalla, S., Chunhapanya, S., Vavruša, M., Verma, T., Wu, P., Fayed, M., Heimerl, K., Sullivan, N., \& Wood, C. (2020). Oblivious DNS over HTTPS (ODoH): A Practical Privacy Enhancement to DNS. arXiv. https://doi.org/10.48550/arXiv.2011.10121}


\bibitem{dns-security-first-version}
 P Mockapetris. 1987. Domain Names - Concepts and Facilities. Technical Report RFC 1034. RFC Editor. 1– 55 pages. https://www.rfc-editor.org/rfc/pdfrfc/rfc1034.txt.pdf

\bibitem{dns-plain-text}
S Bortzmeyer. 2015. DNS Privacy Considerations. RFC 7626. RFC Editor. 1–17 pages. https://tools.ietf.org/html/rfc7626


\bibitem{odoh-rfc-2} E. Kinnear, P. McManus, T. Pauly, T. Verma, and C. A. Wood, ‘Oblivious DNS over HTTPS’, no. 9230. RFC Editor, Jun-2022.


\bibitem{fingerpring-encrypted-dns-1} Hoang, Nguyen, et al. "Domain Name Encryption Is Not Enough: Privacy Leakage via IP-Based Website Fingerprinting." ArXiv, 2021,  https://doi.org/10.48550/arXiv.2102.08332. Accessed 27 Jan. 2023.

\bibitem{fingerpring-encrypted-dns-2} Houser, Rebekah et al. “An investigation on information leakage of DNS over TLS.” Proceedings of the 15th International Conference on Emerging Networking Experiments And Technologies (2019): n. pag.

\bibitem{doh-wikipedia} DNS over HTTPS. (2022, December 14). In Wikipedia. $https://en.wikipedia.org/wiki/DNS_over_HTTPS$

\bibitem{brave-dns} BraveDNS. BraveDNS - A fast, secure, configurable, private DNS + Firewall for Android. https://www.bravedns.com/. (Accessed on 09/16/2020).


\bibitem{cloudflared} Cloudflare. Argo Tunnel Client. https://github.com/cloudfla re/cloudflared, 2020.


\bibitem{acrylic}
Facebook. DNS Over HTTPS Proxy | Facebook. https: //github.com/facebookexperimental/doh-proxy, 2020.

\bibitem{https-size}
Michael Butkiewicz, Harsha V. Madhyastha, and Vyas Sekar. 2011. Understanding
Website Complexity: Measurements, Metrics, and Implications. In Proceedings of
the 2011 ACM SIGCOMM Conference on Internet Measurement Conference (IMC
’11). ACM, 313–328.

\bibitem{https-size2}
B. Newton, K. Jeffay, and J. Aikat. 2013. The Continued Evolution of Web Traffic. In 2013 IEEE 21st International Symposium on Modelling, Analysis and Simulation of Computer and Telecommunication Systems. 80–89.

\bibitem{dns-sizes}
P.V. Mockapetris. 1987. Domain names - implementation and specification. Technical Report RFC1035. RFC Editor. 1–55 pages. https://www.rfc-editor.org/info/ rfc1035


\bibitem{dnssec-adoption}
2022. DNSSEC Validation Rate by country. https://stats.labs.apnic.net/dnssec


\bibitem{dns-vs-https-numb}
Michael Butkiewicz, Harsha V. Madhyastha, and Vyas Sekar. 2011. Understanding website complexity: measurements, metrics, and implications. In Proceedings of the 2011 ACM SIGCOMM conference on Internet measurement conference (IMC '11). Association for Computing Machinery, New York, NY, USA, 313–328. https://doi.org/10.1145/2068816.2068846


\bibitem{dns-message-length} 
A. Mayrhofer. 2016. The EDNS(0) Padding Option. Technical Report RFC7830.
RFC Editor. RFC7830 pages. https://www.rfc-editor.org/info/rfc7830

\bibitem{geni} 
Elliott, Chip. "GENI-global environment for network innovations." LCN. 2008.

\bibitem{wget}
Foundation, F. S. (2010). GNU Wget GNU Wget http://www.gnu.org/software/wget/ .

\bibitem{sslsplit}
Daniel Roethlisberger. 2018. SSLsplit - transparent SSL/TLS interception. https: //www.roe.ch/SSLsplit

\bibitem{feature-qr-length-1}
Marc Liberatore and Brian Neil Levine. 2006. Inferring the source of encrypted HTTP connections. In Proceedings of the 13th ACM conference on Computer and communications security (CCS '06). Association for Computing Machinery, New York, NY, USA, 255–263. https://doi.org/10.1145/1180405.1180437

\bibitem{feature-qr-length-2}
Xiang Cai, Xin Cheng Zhang, Brijesh Joshi, and Rob Johnson. 2012. Touching from a distance: website fingerprinting attacks and defenses. In Proceedings of the 2012 ACM Conference on Computer and Communications Security (CCS ’12). Raleigh, North Carolina, USA.

\bibitem{feature-qr-length-3}
Dominik Herrmann, Rolf Wendolsky, and Hannes Federrath. 2009. Website fingerprinting: attacking popular privacy enhancing technologies with the multinomial naïve-bayes classifier. In Proceedings of the 2009 ACM Workshop on Cloud Computing Security (CCSW ’09). Chicago, Illinois, USA.

\bibitem{feature-qr-length-4}
Andriy Panchenko, Fabian Lanze, Andreas Zinnen, Martin Henze, Jan Pennekamp, Klaus Wehrle, and Thomas Engel. 2016. Website Fingerprinting at Internet Scale. In Proceedings 2016 Network and Distributed System Security Symposium. Internet Society, San Diego, CA.

\bibitem{fingerprinting-by-packet-length}
M. Shen, Y. Liu, S. Chen, L. Zhu and Y. Zhang, "Webpage Fingerprinting using Only Packet Length Information," ICC 2019 - 2019 IEEE International Conference on Communications (ICC), Shanghai, China, 2019, pp. 1-6, doi: 10.1109/ICC.2019.8761167.

\bibitem{total-num-q-r-1}
Hayes, Jamie, and George Danezis. "k-fingerprinting: A Robust Scalable Website Fingerprinting Technique." USENIX security symposium. 2016.

\bibitem{total-num-q-r-2}
Li, S., Guo, H., \& Hopper, N. (2017). Measuring Information Leakage in Website Fingerprinting Attacks and Defenses. ArXiv. https://doi.org/10.48550/arXiv.1710.06080

\bibitem{total-num-q-r-3}
Panchenko, Andriy et al. “Website Fingerprinting at Internet Scale.” Network and Distributed System Security Symposium (2016).

\bibitem{feature-transimission-time-1}
Kevin P. Dyer, Scott E. Coull, Thomas Ristenpart, and Thomas Shrimpton. 2012. Peek-a-Boo, I Still See You: Why Efficient Traffic Analysis Countermeasures Fail. In 2012 IEEE Symposium on Security and Privacy. IEEE, San Francisco, CA, USA, 332–346.

\bibitem{feature-transimission-time-2}
Tao Wang, Xiang Cai, Rishab Nithyanand, Rob Johnson, and Ian Goldberg. 2014. Effective Attacks and Provable Defenses for Website Fingerprinting. In Proceedings of the 23rd USENIX Security Symposium. USENIEX Association, San Diego, CA.

\bibitem{attacker-type}
Claudia Díaz, Stefaan Seys, Joris Claessens, and Bart Preneel. 2003. Towards Measuring Anonymity. In Privacy Enhancing Technologies (PET’03). 54–68.

\bibitem{attacker-wide}
Claudia Díaz, Stefaan Seys, Joris Claessens, and Bart Preneel. 2003. Towards Measuring Anonymity. In Privacy Enhancing Technologies (PET’03). 54–68.

\bibitem{synthetic-data}
Synthetic Data Generation for Machine Learning: A Review" by J. Chen, Y. Yu, Y. Zhang and Y. Liu. IEEE Transactions on Emerging Topics in Computational Intelligence. 2020.

\bibitem{sdv}
Patki, Neha, Roy Wedge, and Kalyan Veeramachaneni. "The synthetic data vault." 2016 IEEE International Conference on Data Science and Advanced Analytics (DSAA). IEEE, 2016.


\bibitem{sdv-for-traffic-analysis-1}
Cordero, Carlos Garcia, et al. "On generating network traffic datasets with synthetic attacks for intrusion detection." ACM Transactions on Privacy and Security (TOPS) 24.2 (2021): 1-39.

\bibitem{sdv-for-traffic-analysis-2}
Xu, S., Marwah, M., Arlitt, M., \& Ramakrishnan, N. (2020). STAN: Synthetic Network Traffic Generation with Generative Neural Models. ArXiv. https://doi.org/10.48550/arXiv.2009.12740


\bibitem{sdv-for-traffic-analysis-2}
Xu, S., Marwah, M., Arlitt, M., \& Ramakrishnan, N. (2020). STAN: Synthetic Network Traffic Generation with Generative Neural Models. ArXiv. https://doi.org/10.48550/arXiv.2009.12740

\bibitem{defence1}
Xiang Cai, Rishab Nithyanand, and Rob Johnson. 2014. CS-BuFLO: A Congestion Sensitive Website Fingerprinting Defense. In Proceedings of the 13th Workshop on Privacy in the Electronic Society (WPES '14). Association for Computing Machinery, New York, NY, USA, 121–130. https://doi.org/10.1145/2665943.2665949

\bibitem{defence2}
K. P. Dyer, S. E. Coull, T. Ristenpart and T. Shrimpton, "Peek-a-Boo, I Still See You: Why Efficient Traffic Analysis Countermeasures Fail," 2012 IEEE Symposium on Security and Privacy, San Francisco, CA, USA, 2012, pp. 332-346, doi: 10.1109/SP.2012.28.


\bibitem{defence-time}
Juarez, Marc, et al. "Toward an Efficient Website Fingerprinting Defense." ArXiv, 2015,  https://doi.org/10.48550/arXiv.1512.00524. Accessed 27 Jan. 2023.

\bibitem{scikit-learn}
F. Pedregosa, G. Varoquaux, A. Gramfort, V. Michel, B. Thirion, O. Grisel, M. Blondel, P. Prettenhofer, R. Weiss, V. Dubourg, J. Vanderplas, A. Passos, D. Cournapeau, M. Brucher, M. Perrot, and E. Duchesnay. 2011. Scikit-learn: Machine Learning in Python. Journal of Machine Learning Research 12 (2011), 2825–2830.

\bibitem{ttl-time}
Giovane C. M. Moura, John Heidemann, Ricardo de O. Schmidt, and Wes Hardaker. 2019. Cache Me If You Can: Effects of DNS Time-to-Live (extended). In Proceedings of the ACM Internet Measurement Conference. ACM, Amsterdam, the Netherlands.

\bibitem{cache-partitioning}
[n.d.]. Mass XS-Search using Cache Attack. https://terjanq.github.io/BugBounty/Google/cache-attack-06jd2d2mz2r0/index.html


%\bibitem{IEEEhowto:kopka}
%H.~Kopka and P.~W. Daly, \emph{A Guide to {\LaTeX}}, 3rd~ed.\hskip 1em plus
% 0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

%\bibitem{lamport} L. Lamport, \emph{ {\LaTeX} A Document Preparation
%  System}, Reading, Mass: Addison-Wesley, 1994.

%\bibitem{knuth} D. E. Knuth, \emph {The \TeX book}, Reading, Mass.:
%  Addison-Wesley, 1996.

\end{thebibliography}